### 2018-07-05 paper/6-engineering.tex
Polish S6.4

\begin{description}
\item[Eviction] The store of traces as shown grows indefinitely, but often
resource constraints require evicting old items from the store. One option is
to evict the contents and any trace that mentions the now-defunct
\hs{Hash}~\hs{v}. However, if the build system can defer materialisation, it
may be possible to only evict the contents, allowing builds to pass-through
hashes of values where the underlying value is not known. If so, the build must
be able to recreate the value if required, potentially dealing with a different
result in a future run.

% \item[Frankenbuilds] A build is considered a
% \emph{frankenbuild}~\cite{esfahani2016cloudbuild} if a value is calculated
% locally, but something that depends on that key is pulled from the cache, and
% the value calculated locally does not match what was previously calculated and
% stored in the cloud. \simon{Don't understand. The explanation in 4.2.4 is better -- and I think describes
% the same thing?}
% Our implementations avoid this issue by storing complete
% traces, but if a cloud build system was to only reference input nodes this
% situation can arise.

\item[Communication] When traces or contents are stored in the cloud
communication can become a bottleneck, so it is important to send only the
minimum amount of information, optimising with respect to build system
invariants. For example, incremental data processing systems in the cloud, such
as \Reflow~\cite{reflow}, need to efficiently orchestrate terabytes of data.

@@

\item[Shallow builds] Sometimes input files will involve many intermediate tasks
before producing the end result, e.g. an installer package. These intermediate
steps may be large, so some cloud build systems are designed to build end
products \emph{without} downloading or \emph{materialising} the results of
intermediate tasks~--~only the final result~--~a so-called \emph{shallow build}.
Some build systems can go even further, integrating with the file system to only
materialise the file when the user accesses it \cite{gvfs}.
\end{description}

>>>>

\begin{description}
\item[Communication] When traces or contents are stored in the cloud,
communication can become a bottleneck, so it is important to send only the
minimum amount of information, optimising with respect to build system
invariants. For example, incremental data processing systems in the cloud, such
as \Reflow~\cite{reflow}, need to efficiently orchestrate terabytes of data.

@@

\item[Eviction] The cloud storage, as modelled
in~\S\ref{sec-constructive-traces}, grows indefinitely, but often resource
constraints require evicting old items from the store. When evicting an old
value \hs{v}, one can also evict all traces mentioning the now-defunct
\hs{hash}~\hs{v}. However, for shallow builds (see below), it is beneficial to
keep these traces, allowing builds to ``pass-through'' hashes whose underlying
values are not known, recreating them only when they must be materialised.

\item[Shallow builds] Building the end result, e.g. an installer package, often
involves many intermediate tasks. The intermediate results may be large, so some
cloud build systems are designed to build end products \emph{without
materialising} intermediate results, producing a so-called \emph{shallow build}
(see an example in~\S\ref{sec-background-bazel}). Some build systems can go even
further, integrating with the file system to only materialise the file when the
user accesses it \cite{gvfs}.
\end{description}
